### 2018-11-07 Sections/mathematical_representation_of_quantum_networks.tex
More indexing
Finished indexing hierarchy

\subsection{Graph-theoretic representation} \index{Network graphs}

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes \cite{???}.

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \textit{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.325\textwidth]{example_routes}
\captionspacefig \caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{example_opt}
\captionspacefig \caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

@@

\subsection{Routing strategies} \label{sec:route_strats} \index{Routing strategies}

>>>>

\subsection{Graph-theoretic representation} \index{Network!Graphs}

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network!Graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes \cite{???}.

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network!Cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \textit{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.325\textwidth]{example_routes}
\captionspacefig \caption{Example of a simple network with multiple routes \mbox{$A\to B$}. Note that $R_3$ and $R_4$ are competing with one another for use of the last link, which the routing strategy, $\mathcal{S}$, will need to resolve if multiple simultaneous transmissions are taking place.} \label{fig:example_routes}
\end{figure}

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{example_opt}
\captionspacefig \caption{The same network graph from Fig.~\ref{fig:example_routes}, with links weighted by some arbitrary cost metric. Applying a shortest-path algorithm yields the optimal route between Alice and Bob to be \mbox{$A\to F\to B$}, which incurs a net cost of \mbox{$c=2$}, as opposed to all other routes, which incur a net cost of \mbox{$c=3$}.} \label{fig:simp_route_opt}
\end{figure}

@@

\subsection{Routing strategies} \label{sec:route_strats} \index{Routing!Strategies}

### 2018-11-07 Sections/optical_encoding_of_quantum_information.tex
Finished indexing hierarchy

\subsection{Single photons} \label{sec:single_phot_enc} \index{Single-photon encoding}

@@

\subsection{Thermal states} \index{Thermal state encoding}\label{sec:thermal_states}

@@

In a non-optical context, the elementary unit of quantum information -- the qubit -- can be naturally encoded into any system with a natural or engineered two-level structure. This actually encompasses a broad range of possibilities, including, amongst many others:
\begin{itemize}
\item \index{2-level systems}Two-level atoms: let two distinct electron energy levels, with long lifetimes, represent the two logical basis states.
\item \index{$\lambda$-configuration systems}$\lambda$-configuration atoms: atoms with two degenerate ground states, which encode the logical qubit, and an additional excited state, which may be transitioned to upon excitation from only one of the ground states. Relaxation from the excited state enables optical coupling via the emitted photon.
\item \index{Quantum dots}Quantum dots: are essentially artificial atoms, which can be engineered with custom band-structures, allowing two- or higher-level qudits to be easily fabricated.
\item \index{Nitrogen-vacancy (NV) centres}Nitrogen-vacancy (NV) centres: are a type of point defect in diamond, which has a very well defined energy level structure that may be utilised to represent qubits.
\item \index{Atomic ensembles}Atomic ensembles: encode quantum information similarly to a single atom, except that the excitation is a \textit{collective} one, in superposition across all the atoms in the ensemble.
\item \index{Superconducting rings}Superconducting rings: a superposition of current flow direction in a superconducting ring represents the two logical basis states.
\item \index{Trapped ions}Trapped ions: qubits are encoded into stable electronic states of electromagnetically trapped ions.
\end{itemize}

>>>>

\subsection{Single photons} \label{sec:single_phot_enc} \index{Single-photons!Encoding}

@@

\subsection{Thermal states} \index{Thermal!State encoding}\label{sec:thermal_states}

@@

In a non-optical context, the elementary unit of quantum information -- the qubit -- can be naturally encoded into any system with a natural or engineered two-level structure. This actually encompasses a broad range of possibilities, including, amongst many others:
\begin{itemize}
\item \index{2-level systems}Two-level atoms: let two distinct electron energy levels, with long lifetimes, represent the two logical basis states.
\item \index{$\lambda$-configuration systems}$\lambda$-configuration atoms: atoms with two degenerate ground states, which encode the logical qubit, and an additional excited state, which may be transitioned to upon excitation from only one of the ground states. Relaxation from the excited state enables optical coupling via the emitted photon.
\item \index{Quantum dots}Quantum dots: are essentially artificial atoms, which can be engineered with custom band-structures, allowing two- or higher-level qudits to be easily fabricated.
\item \index{Nitrogen-vacancy (NV) centres}Nitrogen-vacancy (NV) centres: are a type of point defect in diamond, which has a very well defined energy level structure that may be utilised to represent qubits.
\item \index{Atomic ensembles}Atomic ensembles: encode quantum information similarly to a single atom, except that the excitation is a \textit{collective} one, in superposition across all the atoms in the ensemble.
\item \index{Superconductors!Rings}Superconducting rings: a superposition of current flow direction in a superconducting ring represents the two logical basis states.
\item \index{Trapped ions}Trapped ions: qubits are encoded into stable electronic states of electromagnetically trapped ions.
\end{itemize}

### 2018-11-07 Sections/optimising_the_world.tex
Resized figs for 1 column
Random number fig
Finished indexing hierarchy

Broadly speaking, optimisation problems can all in some sense be thought of as \textit{resource allocation} problems\index{Resource allocation} -- given finite resources, that we would like to utilise most efficiently and for the greatest reward, what is the best way to allocate and distribute them within a complex system?

@@

\comment{To do}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{search_tree}
	\captionspacefig \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how many moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

>>>>

Broadly speaking, optimisation problems can all in some sense be thought of as \textit{resource allocation} problems\index{Resource!Allocation} -- given finite resources, that we would like to utilise most efficiently and for the greatest reward, what is the best way to allocate and distribute them within a complex system?

@@

@@

\begin{figure}[!htbp]
\if 3\pubmode
	\includegraphics[clip=true, width=0.8\textwidth]{search_tree}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{search_tree}
\fi
	\captionspacefig \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how many moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

### 2018-11-07 Sections/physical_architectures_for_quantum_computing.tex
Finished indexing hierarchy

In the continuous-time QW model, a Hamiltonian, $\hat{H}_\mathrm{QW}$, encoding the (Hermitian) adjacency matrix of the QW's graph evolves the walker(s), generating a unitary evolution of the form,
\begin{align}\index{Quantum walk Hamiltonian}
\hat{U}_\mathrm{QW}(t) = e^{-i\hat{H}_\mathrm{QW}t},
\end{align}
where \mbox{$t\in \mathbb{R}_+$}.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.2\textwidth]{QW_arbitrary_graph}
\captionspacefig \caption{A simple example of a quantum walk on an irregular graph structure. Associated with each vertex $x$ is an $\mathrm{SU}(|n_x|)$ coin operator $A^{(x)}$, where $|n_x|$ is the number of neighbours to $x$.} \label{fig:QW_arbitrary_graph}\index{Quantum walk graphs}
\end{figure}

@@

\subsubsection{Encoding quantum information using squeezed states}\index{Squeezed state encoding}

@@

\subsection{Superconducting circuits}\index{Superconducting circuits}\label{sec:artificial_atoms}

@@

One of the most widely used types of artificial atom are superconducting qubits \cite{bib:martinis1985energy, bib:shnirman1997quantum, bib:averin1998adiabatic, bib:devoret2004superconducting, bib:makhlin2001quantum}\index{Superconducting qubits}, a class of non-linear quantum circuits\index{Non-linear quantum circuits}. An LC oscillator\index{LC oscillator} composed of an inductor $L$\index{Inductors} and capacitance $C$\index{Capacitors} is a typical example of a linear quantum circuit\index{Linear quantum circuits} with equal spacing. By introducing a Josephson junction\index{Josephson junction} into the linear quantum circuit we can make it non-linear, with anharmonic energy spectrum.

@@

The flux qubit is popularly known as the RF SQUID (Radio Frequency Superconducting QUantum Interference Device)\index{SQUIDs}, which uses an AC current\index{Alternating current}. This qubit can be considered as the magnetic analogue of the charge qubit. In a charge qubit the Josephson junction is driven by a capacitor, but in a flux qubit, a superconducting transformer\index{Superconducting transformers} circuit generates the flux which drives the circuit. The Hamiltonian of the circuit is,
\begin{align}
\hat{H} = \frac{\hat{q}^{2}}{2 C_{J}} + \frac{\hat\phi^{2}}{2 L} - E_{J} \cos \left( \frac{2e}{\hbar}(\hat\phi - \phi_\mathrm{ext}) \right).
\end{align}

@@

To convert microwave photons to optical photons we can use a quantum transducer. A sketch of a typical design for a quantum transducer\index{Quantum transducer} is shown in Fig.~\ref{fig:quantum_transducer} through a flowchart diagram. The quantum computer is made up of superconducting qubits, which feed quantum information to microwave qubits. The microwave qubits are then interfaced to optical qubits in the visible spectrum through a 3-level quantum system\index{3-level systems}, which can couple at both microwave and optical frequencies. These steps should be reversible. Hence it should be possible to convert the optical qubits back into microwave qubits at the receiving end.

>>>>

In the continuous-time QW model, a Hamiltonian, $\hat{H}_\mathrm{QW}$, encoding the (Hermitian) adjacency matrix of the QW's graph evolves the walker(s), generating a unitary evolution of the form,
\begin{align}\index{Quantum walks!Hamiltonian}
\hat{U}_\mathrm{QW}(t) = e^{-i\hat{H}_\mathrm{QW}t},
\end{align}
where \mbox{$t\in \mathbb{R}_+$}.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.2\textwidth]{QW_arbitrary_graph}
\captionspacefig \caption{A simple example of a quantum walk on an irregular graph structure. Associated with each vertex $x$ is an $\mathrm{SU}(|n_x|)$ coin operator $A^{(x)}$, where $|n_x|$ is the number of neighbours to $x$.} \label{fig:QW_arbitrary_graph}\index{Quantum walk!Graphs}
\end{figure}

@@

\subsubsection{Encoding quantum information using squeezed states}\index{Squeezed states!Encoding}

@@

\subsection{Superconducting circuits}\index{Superconductors!Circuits}\label{sec:artificial_atoms}

@@

One of the most widely used types of artificial atom are superconducting qubits \cite{bib:martinis1985energy, bib:shnirman1997quantum, bib:averin1998adiabatic, bib:devoret2004superconducting, bib:makhlin2001quantum}\index{Superconductors!Qubits}, a class of non-linear quantum circuits\index{Non-linear quantum circuits}. An LC oscillator\index{LC oscillator} composed of an inductor $L$\index{Inductors} and capacitance $C$\index{Capacitors} is a typical example of a linear quantum circuit\index{Linear quantum circuits} with equal spacing. By introducing a Josephson junction\index{Josephson junction} into the linear quantum circuit we can make it non-linear, with anharmonic energy spectrum.

@@

The flux qubit is popularly known as the RF SQUID (Radio Frequency Superconducting QUantum Interference Device)\index{SQUIDs}, which uses an AC current\index{Alternating current}. This qubit can be considered as the magnetic analogue of the charge qubit. In a charge qubit the Josephson junction is driven by a capacitor, but in a flux qubit, a superconducting transformer\index{Superconductors!Transformers} circuit generates the flux which drives the circuit. The Hamiltonian of the circuit is,
\begin{align}
\hat{H} = \frac{\hat{q}^{2}}{2 C_{J}} + \frac{\hat\phi^{2}}{2 L} - E_{J} \cos \left( \frac{2e}{\hbar}(\hat\phi - \phi_\mathrm{ext}) \right).
\end{align}

@@

To convert microwave photons to optical photons we can use a quantum transducer. A sketch of a typical design for a quantum transducer\index{Quantum transducers} is shown in Fig.~\ref{fig:quantum_transducer} through a flowchart diagram. The quantum computer is made up of superconducting qubits, which feed quantum information to microwave qubits. The microwave qubits are then interfaced to optical qubits in the visible spectrum through a 3-level quantum system\index{3-level systems}, which can couple at both microwave and optical frequencies. These steps should be reversible. Hence it should be possible to convert the optical qubits back into microwave qubits at the receiving end.

### 2018-11-07 Sections/protocols_for_the_quantum_internet.tex
Finished indexing hierarchy

\subsection{Single-photons} \label{sec:single_phot_src} \index{Single-photon state preparation}

@@

\subsection{Squeezed states} \label{sec:squeezed} \index{Squeezed state preparation}

@@

\subsubsection{Superconducting photo-detectors}\index{Superconducting photo-detectors}

@@

\subsubsection{Quantum dot photo-detectors}\index{Quantum dot photo-detectors}

@@

Photo-detectors of all types are inevitably subject to `dark-counts'\index{Dark-counts}, whereby thermal noise\index{Thermal noise}, either within the detector or coupled from the noisy external environment, triggers non-existent detection events. The distribution follows exactly that of the thermal state photon-number distribution (Sec.~\ref{sec:thermal_states}). Thus, the probability of $n$ dark-counts occurring is,
\begin{align} \index{Thermal distribution}
p_\mathrm{dc}(n) = e^{-|\alpha|^2} \frac{|\alpha|^2}{n!},
\end{align}
where $\alpha$ is a parameterisation of the temperature of the environmental noise. Fortunately, modern detector technology is able to keep dark-count rates very low, making this far less of an issue than the aforementioned ones, loss being the dominant.

@@

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using: two-level\index{Two-level atoms} or $\lambda$-configuration atoms\index{$\lambda$-configuration systems}; superconducting rings\index{Superconducting rings}; ion traps\index{Ion traps}; atomic ensembles\index{Atomic ensembles}; and countless more.

@@

An alternate approach is to use W-state encoding\index{W-state encoding} to implement unitary error averaging (Sec.~\ref{sec:error_averaging})\index{Unitary error averaging}, where the unitaries are single-qubit channels \cite{errorfilteringpaper, bib:MadhavPeterLund}. The protocol is shown in Fig.~\ref{fig:W_state_memory}. We begin by using a QFT fanout\index{Fanout} operation to encode a dual-rail encoded qubit\index{Dual-rail encoding} across $N$ optical modes. Each optical mode then feeds into a solid-state qubit (e.g a two-level atom), which ideally implement an identity channel but are inevitably subject to usual error processes such as dephasing and amplitude damping (characterised by $T_1$- and $T_2$-times\index{T$_2$-time}\index{T$_1$-time}). Finally, the inverse fanout operation is applied and success of the protocol is defined as there being exactly one photon between the first two (`success') output modes. If a photon is detected in any of the other (`failure') modes the state is presumed erroneous and discarded.

@@

This scenario is an obvious example of where a UDP-like \textsc{Send-and-forget} protocol may be viable. Unlike most other applications, Bob is broadcasting a stream of identical, pure quantum states, that are not entangled with any peripheral system, and are easily replicated, with no correlations between distinct photons. Thus, if any particular photon fails to reach Alice, it matters not, as she can simply await the next one emanating from Bob's bombardment of photons (the `shotgun' approach\index{Shotgun protocol}). There are no QoS requirements.

>>>>

\subsection{Single-photons} \label{sec:single_phot_src} \index{Single-photon!Preparation}

@@

\subsection{Squeezed states} \label{sec:squeezed} \index{Squeezed states!Preparation}

@@

\subsubsection{Superconducting photo-detectors}\index{Superconductors!Photo-detectors}

@@

\subsubsection{Quantum dot photo-detectors}\index{Quantum dots!Photo-detectors}

@@

Photo-detectors of all types are inevitably subject to `dark-counts'\index{Dark-counts}, whereby thermal noise\index{Thermal!Noise}, either within the detector or coupled from the noisy external environment, triggers non-existent detection events. The distribution follows exactly that of the thermal state photon-number distribution (Sec.~\ref{sec:thermal_states}). Thus, the probability of $n$ dark-counts occurring is,
\begin{align} \index{Thermal!Distribution}
p_\mathrm{dc}(n) = e^{-|\alpha|^2} \frac{|\alpha|^2}{n!},
\end{align}
where $\alpha$ is a parameterisation of the temperature of the environmental noise. Fortunately, modern detector technology is able to keep dark-count rates very low, making this far less of an issue than the aforementioned ones, loss being the dominant.

@@

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using: two-level\index{2-level atoms} or $\lambda$-configuration atoms\index{$\lambda$-configuration systems}; superconducting rings\index{Superconductors!Rings}; ion traps\index{Ion traps}; atomic ensembles\index{Atomic ensembles}; and countless more.

@@

An alternate approach is to use W-state encoding\index{W-states!Encoding} to implement unitary error averaging (Sec.~\ref{sec:error_averaging})\index{Unitary error averaging}, where the unitaries are single-qubit channels \cite{errorfilteringpaper, bib:MadhavPeterLund}. The protocol is shown in Fig.~\ref{fig:W_state_memory}. We begin by using a QFT fanout\index{Fanout} operation to encode a dual-rail encoded qubit\index{Dual-rail encoding} across $N$ optical modes. Each optical mode then feeds into a solid-state qubit (e.g a two-level atom), which ideally implement an identity channel but are inevitably subject to usual error processes such as dephasing and amplitude damping (characterised by $T_1$- and $T_2$-times\index{T$_2$-time}\index{T$_1$-time}). Finally, the inverse fanout operation is applied and success of the protocol is defined as there being exactly one photon between the first two (`success') output modes. If a photon is detected in any of the other (`failure') modes the state is presumed erroneous and discarded.

@@

This scenario is an obvious example of where a UDP-like \textsc{Send-and-forget} protocol may be viable. Unlike most other applications, Bob is broadcasting a stream of identical, pure quantum states, that are not entangled with any peripheral system, and are easily replicated, with no correlations between distinct photons. Thus, if any particular photon fails to reach Alice, it matters not, as she can simply await the next one emanating from Bob's bombardment of photons (the `shotgun' approach\index{Shotgun!Protocol}). There are no QoS requirements.

### 2018-11-07 Sections/quality_of_service.tex
Finished indexing hierarchy

\subsection{Stabiliser codes}\index{Stabiliser codes}\label{sec:stab_code}

@@

The most common topological code, which we will use here as an example, is the toric code\index{Toric code}, which resides on a lattice graph over the surface of a torus\footnote{As with cluster states, this graph needn't (but could) correspond to a network graph.}. As with cluster states (Sec.~\ref{sec:CSQC}), the toric code is most easily visualised in the stabiliser formalism\index{Stabiliser formalism}, and the toric code is an example of a stabiliser code\index{Stabiliser codes} (Sec.~\ref{sec:stab_code}). Consider a rectangular sub-graph of the torus. We place a qubit on each edge (not vertex) of the graph. Now we define two sets of stabiliser operators: \textit{star} ($\hat{S}_+$) and \textit{plaquette} ($\hat{S}_\square$) operators,
\begin{align} \index{Surface code stabilisers}\index{Star operator}\index{Plaquette operator}
	\hat{S}_+(v) &= \prod_{i\in e(v)} \hat{X}_i, \nonumber \\
	\hat{S}_\square(p) &= \prod_{i\in e(p)} \hat{Z}_i,
\end{align}
where $e(v)$ are the edges neighbouring vertex $v$, and $e(p)$ are the edges surrounding plaquette $p$. By definition, the toric code state, $\ket\psi_\mathrm{toric}$, satisfies the stabiliser relations,
\begin{align}
	\hat{S}_+(v) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, v, \nonumber \\
	\hat{S}_\square(p) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, p.
\end{align}
The stabilisers can be visualised graphically as per Fig.~\ref{fig:toric_code}.

@@

\subsection{Qubit loss codes}\index{Qubit loss codes}

@@

First CV QEC protocol is the direct analogue of the the qubit redundancy codes. However, the noise models do not correspond to what usually occur in Gaussian systems, namely, thermal noise\index{Thermal noise} and loss.

>>>>

\subsection{Stabiliser codes}\index{Stabiliser!Codes}\label{sec:stab_code}

@@

The most common topological code, which we will use here as an example, is the toric code\index{Toric code}, which resides on a lattice graph over the surface of a torus\footnote{As with cluster states, this graph needn't (but could) correspond to a network graph.}. As with cluster states (Sec.~\ref{sec:CSQC}), the toric code is most easily visualised in the stabiliser formalism\index{Stabiliser!Formalism}, and the toric code is an example of a stabiliser code\index{Stabiliser!Codes} (Sec.~\ref{sec:stab_code}). Consider a rectangular sub-graph of the torus. We place a qubit on each edge (not vertex) of the graph. Now we define two sets of stabiliser operators: \textit{star} ($\hat{S}_+$) and \textit{plaquette} ($\hat{S}_\square$) operators,
\begin{align} \index{Surface code stabilisers}\index{Star operator}\index{Plaquette operator}
	\hat{S}_+(v) &= \prod_{i\in e(v)} \hat{X}_i, \nonumber \\
	\hat{S}_\square(p) &= \prod_{i\in e(p)} \hat{Z}_i,
\end{align}
where $e(v)$ are the edges neighbouring vertex $v$, and $e(p)$ are the edges surrounding plaquette $p$. By definition, the toric code state, $\ket\psi_\mathrm{toric}$, satisfies the stabiliser relations,
\begin{align}
	\hat{S}_+(v) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, v, \nonumber \\
	\hat{S}_\square(p) \ket\psi_\mathrm{toric} &= \ket\psi_\mathrm{toric} \,\forall\, p.
\end{align}
The stabilisers can be visualised graphically as per Fig.~\ref{fig:toric_code}.

@@

\subsection{Qubit loss codes}\index{Qubit loss!Codes}

@@

First CV QEC protocol is the direct analogue of the the qubit redundancy codes. However, the noise models do not correspond to what usually occur in Gaussian systems, namely, thermal noise\index{Thermal!Noise} and loss.

### 2018-11-07 Sections/quantum_algorithms.tex
Finished indexing hierarchy

The phase-estimation algorithm is not extremely useful as a standalone product, but acts as a necessary subroutine in many important algorithms, such as Shor's algorithm\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}) and topological data analysis\index{Topological data analysis} (Sec.~\ref{sec:TDA}).

@@

\subsection{Topological data analysis} \index{Topological data analysis}\label{sec:TDA}

@@

One avenue for the analysis of large, complex datasets is via homology theory\index{Homology theory}, which yields \textit{topological data analysis} (TDA)\index{Topological data analysis}. In particular, the so-called \textit{Betti numbers}\index{Betti numbers} characterise the nature of interconnectedness within a dataset. Specifically, the $k$th Betti number, $\beta_k$, is the number of $k$-dimensional holes and voids in a dataset. For example, $\beta_0$, $\beta_1$ and $\beta_2$ represents the number of connected components, 1-dimensional holes, and 2-dimensional voids in a dataset respectively.

>>>>

The phase-estimation algorithm is not extremely useful as a standalone product, but acts as a necessary subroutine in many important algorithms, such as Shor's algorithm\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}) and topological data analysis\index{Topological!Data analysis} (Sec.~\ref{sec:TDA}).

@@

\subsection{Topological data analysis} \index{Topological!Data analysis}\label{sec:TDA}

@@

One avenue for the analysis of large, complex datasets is via homology theory\index{Homology theory}, which yields \textit{topological data analysis} (TDA)\index{Topological!Data analysis}. In particular, the so-called \textit{Betti numbers}\index{Betti numbers} characterise the nature of interconnectedness within a dataset. Specifically, the $k$th Betti number, $\beta_k$, is the number of $k$-dimensional holes and voids in a dataset. For example, $\beta_0$, $\beta_1$ and $\beta_2$ represents the number of connected components, 1-dimensional holes, and 2-dimensional voids in a dataset respectively.

### 2018-11-07 Sections/quantum_repeater_networks.tex
Finished indexing hierarchy

\subsubsection{Performance}\index{Repeater performance}

@@

\subsection{Resource scalings across repeater generations}\index{Resource scaling}

@@

\subsection{Repeater synchronisation}\index{Repeater synchronisation}\index{Race-time conditions}

>>>>

\subsubsection{Performance}\index{Repeater!Performance}

@@

\subsection{Resource scalings across repeater generations}\index{Resource!Scaling}

@@

\subsection{Repeater synchronisation}\index{Repeater!Synchronisation}\index{Race-time conditions}

### 2018-11-07 Sections/routing_strategies.tex
Adding image cropping
Finished indexing hierarchy

\section{Routing strategies} \label{sec:strategies} \index{Routing strategies}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{conflict}
\captionspacefig \caption{A simple network with two competing pairs of senders and receivers, \mbox{$A_1\to B_1$} and \mbox{$A_2\to B_2$}. Edges are labelled by \mbox{$\{b,d\}$}, where $b$ is the bandwidth attribute of the link (i.e number of states that can be communicated simultaneously), and $d$ is the cost metric associated with the link, e.g loss in dB. (blue line) $R_1$ and $R_2$ are two routes from $A_2\to B_2$. Either of these routes could be declared optimal, depending on the choice of cost function. For a trivial additive cost function, $R_2$ would be declared optimal. (red lines) $R_3$ is the optimal route from \mbox{$A_1\to B_1$}.} \label{fig:conflict}
\end{figure}

@@

\subsection{Round robin} \label{sec:round_robin} \index{Round robin strategies}

>>>>

\section{Routing strategies} \label{sec:strategies} \index{Routing!Strategies}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{conflict}
\captionspacefig \caption{A simple network with two competing pairs of senders and receivers, \mbox{$A_1\to B_1$} and \mbox{$A_2\to B_2$}. Edges are labelled by \mbox{$\{b,d\}$}, where $b$ is the bandwidth attribute of the link (i.e number of states that can be communicated simultaneously), and $d$ is the cost metric associated with the link, e.g loss in dB. (blue line) $R_1$ and $R_2$ are two routes from $A_2\to B_2$. Either of these routes could be declared optimal, depending on the choice of cost function. For a trivial additive cost function, $R_2$ would be declared optimal. (red lines) $R_3$ is the optimal route from \mbox{$A_1\to B_1$}.} \label{fig:conflict}
\end{figure}

@@

\subsection{Round robin} \label{sec:round_robin} \index{Round-Robin!Strategies}
